---
title: 'Mining Lalibela: Part 1'
author: "Awash Analytics"
date: "21 Dec 2017"
output: html_document
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: DarkRed;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
  margin-bottom: 50px;
}

div.screenshot {
  width: 950px;
  height: 350px;
  margin-top: 30px;
  margin-bottom: 125px;
}

p {
  margin-top: 20px;
  margin-bottom: 20px;
}

div.img {
  margin-top: 20px;
  margin-bottom: 20px;
}

div.myCaption {
  margin-top: 10px;
  margin-bottom: 3px;
}

</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div id="intro">
<!-- <h4>1. Introduction</h4> -->
## Introduction

<p>
In this article I explain how I managed to scrape <a target="_blank" href="https://www.tripadvisor.com/Attractions">TripAdvisor</a> reviews for attraction sites (e.g., Lalibela, Ethiopia and Louvre museum, Paris). The R program manages to scape important review attributes such as review title, date, device (used to post a review, e.g., mobile), and reviewer's country of residence. The title, for example, is an interesting attribute to perform a sentiment analysis. Let's get started.
</p>

</div> <!-- end introduction -->

<div id="get_10Reviews-area">
<!-- <h4>2. Scraping TripAdvisor Review Components</h4> -->
## Scraping the Main Attributes

<p>
The ``get_10Reviews()`` function shown below extracts the required components / attributes of a review such as review title, description, date, name, location, and device. For the CSS selector, I used a tool called <a target="_blank" href="https://chrome.google.com/webstore/detail/selectorgadget/mhjhnkcfbdhnjickkkdbjoemdmbfginb?hl=en">SelectorGadget</a>. For the web scraping part I mainly used the ``rvest`` package - Thanks to Hadley Wickham!

The ``get_10Reviews`` function has one argument called "node". This represents a single review given by the user, and its value is set by the other program which will be discussed later.

For text processing I used the ``stringr`` package. When I scrape the review date, for example, an extra character ("Reviewed") was returned togther with the review date Thus, as shown in the code below I used ``stringr::str_replace`` function to remove the extra string as we're only interested with the date.

The ``rvest`` package returns "0" when no value is returned from the web (e.g., the user's country of residence is not filled in his/her profile). That is the reason for using the ``ifelse`` function in the last part of the code below. This ensures that the number of reviews posted in the TripAdvisor site and the one read by R is the same. Otherwise, less number of reviews will be read by R because of the missing attributes. I hope this issue will be resolved by the developer of the ``rvest`` package soon.
</p>

<div class="myCaption">
*Code 1: The R program responsible for grabbing the required components of a given review (e.g., reviewer title, date, device, location, etc).*
</div>
```{r, eval=FALSE}
#' 
#' Extracts all components of a review such as review title, date, location, device, etc.
#' 
#' @param node the single review given by a user
#' 
#' @references 
#' Inspired by Hadley Wickham (author of pkg::rvest) and BjaRule (StackOverflow).
#' https://github.com/hadley/rvest/issues/12
#' https://stackoverflow.com/questions/33250826/scraping-with-rvest-complete-with-nas-when-tag-is-not-present
#' 
#' @author Awash Analytics (December 2017)
#' 
#' @seealso The main program get_allReviews.R make use of this program to extract all the components of a given review.
#' 
#' 

get_10Reviews <- function(node) {

  ## Get current node/row
  node_current <- node
  
  ##########################
  ## Extract all columns  ##
  ##########################
  ## review title
  tmp_title <- node_current %>%
    rvest::html_node(".noQuotes") %>%
    rvest::html_text() 
  
  ## review title
  tmp_fullReview <- node_current %>%
    rvest::html_node(".partial_entry") %>%
    rvest::html_text() 
  
  ## review date
  tmp_date <- node_current %>%
    rvest::html_node(".relativeDate") %>%
    rvest::html_text() %>%
    stringr::str_replace(pattern = "(Reviewed)", replacement = "") %>%   ## removes the text "reviews"
    stringr::str_trim() 
  
  ## reviewer username
  tmp_userName <- node_current %>%
    rvest::html_node(".scrname") %>%
    rvest::html_text()
  
  ## reviewer location
  tmp_userLocation <- node_current %>%
    rvest::html_node(css = ".userLocation") %>%
    html_text()
  
  ## reviewer country of origin, probably a city
  tmp_device <- node_current %>%
    rvest::html_node(".viaMobile") %>%
    rvest::html_text()
  
  ##############################################################
  ## Create final dataframe.                                  ##
  ##############################################################
  ## ** A null value is filled whenever no value is returned  ##
  ##    from Web Scrapping step.                              ##
  ##############################################################
  data.frame(
    title = ifelse(length(tmp_title) == 0, NA,       ## the IFELSE function is used to fill NA whenever HTML_NODES is not able to return a value
                   tmp_title),
    full_review = ifelse(length(tmp_fullReview) == 0, NA,
                         tmp_fullReview),
    date = ifelse(length(tmp_date) == 0, NA,
                  tmp_date),
    user_name = ifelse(length(tmp_userName) == 0, NA,
                      tmp_userName),
    user_device = ifelse(length(tmp_device) == 0, NA,
                    tmp_device),
    user_location = ifelse(length(tmp_userLocation) == 0, NA,      
                                 tmp_userLocation),
    stringsAsFactors=F
  )
}
```
</div> <!-- get_10Reviews-area -->


<div id="get_allReviews-area">
<!-- <h4>3. How to scrap all reviews (in a page or multiple pages)?</h4> -->
## Scraping All Reviews

<p>
The above code handles an individual review at a time and extracts the required attributes of the review. However, there are a total of ten (10) reviews per page. For example, see here <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">TripAdvisor - Lalibela</a>. 

The ``get_allReviews()`` function shown below is developed to loop through the required number of pages. The number of pages is set by the user using the "nbr_page" argument of the function. 

The values of the other arguments (such as "site_gCode", "site_dCode", "site_name", and "site_geoLocation") are available for you in the url of the attraction site that you're interested to grab reviews from. For <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">TripAdvisor - Lalibela</a> attraction site, for example, the parameter values will be: ``site_gCode = "480193"``, ``site_dCode = "324957"``, ``site_name = "Rock_Hewn_Churches_of_Lalibela"``, and ``site_geoLocation = "Lalibela_Amhara_Region"``. In the application section, I used different attraction sites (e.g., Louvre museum, Paris and Mount Kenya, Kenya) to show you usage of the R programs and how to set the input parameters. 
</p>


<div class="myCaption">
*Code 2: The R program responsible for grabbing all reviews available in a single page or multiple pages.*
</div>
```{r, eval=FALSE}
#' 
#' Extracts reviews of an attraction site posted by tourists on TripAdvisor website.
#' It takes care of both a single page and multiple pages.
#' 
#' @param nbr_page the number of pages to grab.
#' @param site_gCode the "g" code as defined by TripAdvisor pagination. Please see the example below.
#' @param site_dCode the "d" code as defined by TripAdvisor pagination. Please see the example below.
#' @param site_name the name of an attraction site.
#' @param site_geoLocation the geographical location of an attraction site. Not that this is not related to a latitude/longitude values. Please see the example below.
#' 
#' @describe This source code calls get_10Reviews.R program to extract the required components (e.g., review title, date, device). Depending on
#' a user request, it can also loop through multiple pages. Finally, it adds extra columns (e.g., attraction location, number of reviews, etc) 
#' to existing reviews stored in a dataframe.
#' 
#' @author Awash Analytics (December 2017)
#' 
#' @example reviews_lalibela <- get_allReviews(nbr_page = 2, 
#'                                             site_gCode = "480193", site_dCode = "324957", 
#'                                             site_name = "Rock_Hewn_Churches_of_Lalibela", site_geoLocation = "Lalibela_Amhara_Region"
#'                                             )
#' 

get_allReviews <- function(nbr_page = NULL, 
                           site_gCode = NULL, site_dCode = NULL, 
                           site_name = NULL, site_geoLocation = NULL) {
  
  message("Page extraction is started: ", date())
  
  ## Main TripAdvisor URL
  TripAdvisor_url <- "https://www.tripadvisor.com"
  
  ## loop through reviews page
  for (i in 1:nbr_page) {
    # print(paste("i = ", i, sep = " "))       ## used only for debugging purpose
    
    ## Construct url address associated to the reviews page
    url_extCommon <- paste("/Attraction_Review-g", site_gCode, "-d", site_dCode, "-Reviews-", 
                           sep = "") 
    
    if (i == 1) {
      # reviewHomePg <- "/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region"
      reviewHomePg <- paste(url_extCommon,
                            site_name, "-", site_geoLocation, 
                            sep = "")
      
      TripAdvisor_reviewUrl <- paste(TripAdvisor_url, reviewHomePg, ".html", 
                                           sep = "") 
      
      ## Backup review home address for later use
      TripAdvisor_reviewHomeUrl <- TripAdvisor_reviewUrl
    } 
    else {
      # reviewOtherPg <- paste("/Attraction_Review-g480193-d324957-Reviews-or", i-1, "0-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region",
      #                                 sep = "")
      reviewOtherPg <- paste(url_extCommon, 
                             "or", i-1, "0-", 
                             site_name, "-", site_geoLocation, 
                             sep = "")
      
      TripAdvisor_reviewUrl <- paste(TripAdvisor_url, reviewOtherPg, ".html",
                                           sep = "")
    }
    
    ## Read reviews given about an attraction site 
    TripAdvisor_topic <- xml2::read_html(TripAdvisor_reviewUrl)
    
    ## Get main container which contains a single review
    reviewer_container <- TripAdvisor_topic %>%
      html_nodes("div.review-container")
    
    ## Get all components of reviews (e.g., title, location, device, etc) and loop through the ten (10) reviews
    reviews_data <- lapply(X = reviewer_container, get_10Reviews) %>%
      dplyr::bind_rows()
    
    ## Concatenate reviews obtained from all pages
    if (i == 1) {
      reviews_dataAll = data.frame(page_nbr = i, reviews_data)
    } else {
      reviews_dataAll <- rbind(reviews_dataAll, 
                               data.frame(page_nbr = i, reviews_data))
    }
  }
  
  #############################################################################################################################
  ## Combine reviews data with other variables available in review homepage (e.g., number of reviews, site location, etc).   ##
  #############################################################################################################################
  # TripAdvisor_homePage <- "https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html"
  TripAdvisor_reviewHome <- xml2::read_html(TripAdvisor_reviewHomeUrl)
  
  ## Get total number of reviews given for an attraction site
  total_reviews <- TripAdvisor_reviewHome %>%
    rvest::html_nodes(".seeAllReviews") %>%
    rvest::html_text() %>%
    stringr::str_replace_all(pattern = "(reviews)|(\\\nRead\\s+(all))", replacement = "") %>%   ## removes the text "reviews"
    stringr::str_trim() %>%
    stringr::str_replace(pattern = ",", replacement = "") %>%           ## removes the comma
    as.numeric() %>%
    dplyr::first()          ## In case, multiple values are returned (e.g., "204", "204" which is true for Axum, Ethiopia)
  
  ## get attraction site location
  attraction_location <- TripAdvisor_reviewHome %>%
    rvest::html_node(".address") %>%
    rvest::html_text() 
  
  ## Date for data access
  date_dataAccess <- Sys.Date() %>%
    format(format = "%B %d, %Y")          ## this gives date format like "December 21, 2017"
  
  ## Combine main reviews data and additional info about the site
  reviews_final <- data.frame(attraction_location, total_reviews, 
                              date_dataAccess, reviews_dataAll 
  )
  
  message("Page extraction is completed: ", date())
  
  return(reviews_final)
}
```

</div> <!-- get_allReviews-area -->


<div id="main-application-area">
<!-- <h4>4. Application</h4> -->
## Application

<p>
Now I'll explain usage of the functions I built for scraping <a target="_blank" href="https://www.tripadvisor.com/Attractions">TripAdvisor</a> using three attraction sites such as <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">Lalibela - Ethiopia</a>, <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g187147-d188757-Reviews-Louvre_Museum-Paris_Ile_de_France.html">Louvre museum - Paris</a> and <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g319715-d1936998-Reviews-Mount_Kenya-Mount_Kenya_National_Park.html">Mount Kenya - Kenya</a>.

As shown in the code below, the dependence packages should be installed and loaded. Then, the two R source codes (i.e., ``get_10Reviews.R`` and ``get_allReviews_v2.R``) should be loaded to R using the ``source()`` function. Now the scraper functions I discussed before are ready for use.

<div class="myCaption">
*Code 3: The main R program which shows usage of the scraper functions. For demonstration purpose, three attraction sites are selected: Lalibela, Louvre museum and Mount Kenya.*
</div>

```{r, eval=TRUE, message=F, warning=F}
################################
## Environmental settings.    ##
################################
## Set the working directory
# setwd("./TripAdvisor/tourism/")

## Install and load library
library(xml2)         ## to use the READ_HTML function
library(rvest)        ## for all other utilities used for Web Scrapping. Please see package documentation
library(stringr)      ## for regular expression (regex)
library(readr)        ## for import/export of data
library(dplyr)        ## for data manipulation
library(magrittr)     ## for the pipe operator

# options(knitr.table.format = "markdown")
options(knitr.table.format = "html")

###################################################
## Reading reviews of an attraction site.       ##
###################################################
## Load scraper source codes
source("./functions/get_10Reviews.R")
source("./functions/get_allReviews_v2.R")

## Get reviews about Lalibela, Ethiopia
reviews_lalibela <- get_allReviews(nbr_page = 2, 
                                   site_gCode = "480193", site_dCode = "324957", 
                                   site_name = "Rock_Hewn_Churches_of_Lalibela", 
                                   site_geoLocation = "Lalibela_Amhara_Region"
                                   )
```

I'll first show how I scraped <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">Lalibela - Ethiopia</a>. The url of Lalibela is: <https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html>. The url has everything we need to run the scraper function. As shown in the code above, the input parameters are set to the following values: ``site_gCode = "480193"``, ``site_dCode = "324957"``, ``site_name = "Rock_Hewn_Churches_of_Lalibela"``, and ``site_geoLocation = "Lalibela_Amhara_Region"``.   
</p>

<p>
The above code returns the result shown below in Table 1 after scraping <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">Lalibela - Ethiopia</a>. Only eight (8) out of twenty (20) records are displayed in the table. The first reviewer was from Colorado, USA who posted his/her review via mobile device four days ago. The last reviewer was from UK and he/she posted her review on 22 October 2017 using other devices (e.g., laptop). A total of 1,434 reviews has been posted on <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">TripAdvisor - Lalibela</a>. 
</p>

<div class="myCaption">
*Table 1. Tourist reviews about Lalibela, Ethiopia.*
</div>
```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_lalibela[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```

<p>
The second attraction site I used for this article is <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g187147-d188757-Reviews-Louvre_Museum-Paris_Ile_de_France.html">Louvre museum - Paris</a>. Who doesn't know Mona Lisa? This is the url used by TripAdvisor to store tourist reviews about Louvre museum: <https://www.tripadvisor.com/Attraction_Review-g187147-d188757-Reviews-Louvre_Museum-Paris_Ile_de_France.html>. As shown in the function call below, values that are set for the input parameters are exactly the same as we see in the url. 
</p>

<div class="myCaption">
*Code 4: Reading TripAdvisor reviews about Louvre museum, France.*
</div>
```{r, eval=TRUE, message=F}
## Get reviews about Louvre Museum, Paris, France
reviews_louvreMuseum <- get_allReviews(nbr_page = 2, 
                                       site_gCode = "187147", site_dCode = "188757", 
                                       site_name = "Louvre_Museum", 
                                       site_geoLocation = "Paris_Ile_de_France"
                                       )
```

<p>
Table 4 below shows part of the reviews that was scraped from TripAdvisor about Louvre museum, Paris, France. The first reviewer was from New Delhi, India and the review was posted yesterday. The last reviewer was from Melbourne, Australia. A total of 80,774 reviews has ben posted on <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g187147-d188757-Reviews-Louvre_Museum-Paris_Ile_de_France.html">TripAdvisor - Louvre museum</a>.
</p>

<div class="myCaption">
*Table 4. Tourist reviews about Louvre museum, France.*
</div>
```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_louvreMuseum[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```

<p>
Finally, let's take our flight from Paris to Kenya and try to understand the impression of tourists about <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g319715-d1936998-Reviews-Mount_Kenya-Mount_Kenya_National_Park.html">Mount Kenya - Kenya</a>. The url of Mount Kenya in TripAdvisor is: <https://www.tripadvisor.com/Attraction_Review-g319715-d1936998-Reviews-Mount_Kenya-Mount_Kenya_National_Park.html>.
</p>

<div class="myCaption">
*Code 5: Reading TripAdvisor reviews about Mount Kenya, Kenya*
</div>
```{r, eval=TRUE, message=F}
## Get reviews about Mount Kenya, Kenya
reviews_mountKenya <- get_allReviews(nbr_page = 2, 
                                     site_gCode = "319715", site_dCode = "1936998", 
                                     site_name = "Mount_Kenya", 
                                     site_geoLocation = "Mount_Kenya_National_Park"
                                     )
```

<p>
As shown in the last column of Table 3, it's interesting to see that tourists come to Mount Kenya from all over the world, ranging from Cairo, Egypt to Copenhagen, Denmark and to Ghent, Belgium. A total of 352 reviews has been posted on <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g319715-d1936998-Reviews-Mount_Kenya-Mount_Kenya_National_Park.html">TripAdvisor - Mount Kenya</a>.
</p>

<div class="myCaption">
*Table 3. Tourist reviews about Mount Kenya, Kenya.*
</div>
```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_mountKenya[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```

</div>  <!-- end main-application-area -->

<!-- <h4>5. Conclusion</h4> -->
## Conclusion
<p>
I hope you find this article useful. I also believe that with a minor modification the same source code can be used to scrap reviews about other services such as restaurant, hotel, etc. 

Good luck and Happy to hear your opinion. Thanks! 
</p>


