---
title: 'Mining Lalibela: Part 1'
author: "Awash Analytics"
date: "21 Dec 2017"
output: html_document
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: DarkRed;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
  margin-bottom: 50px;
}

div.screenshot {
  width: 950px;
  height: 350px;
  margin-top: 30px;
  margin-bottom: 125px;
}

p {
  margin-top: 20px;
  margin-bottom: 20px;
}

div.img {
  margin-top: 20px;
  margin-bottom: 20px;
}

</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div id="intro">
<h4>Introduction</h4>
<p>
In this blog post, I would like to show you how I scrapped TripAdvisor user reviews for one of tourist destination place in Ethiopia called Lalibela. This is the link for the reviews:
<https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html>
</p>
</div> <!-- end introduction -->

<div id="mainRCode-area">

<h4> The Main R Source Code</h4>

```{r, eval=FALSE}
test
```

```{r, eval=FALSE}
test
```

</div> <!-- mainRCode-area -->

<div id="get_10Reviews-area">
<h4>Reading the Ten (10) Reviews</h4>


```{r, eval=FALSE}
test
```
</div> <!-- get_10Reviews-area -->

<div id="get_allReviews-area">
<h4>Looping through all pages</h4>

```{r, eval=FALSE}
test
```


</div> <!-- get_allReviews-area -->



```{r, eval=FALSE}
test
```
