---
title: 'Mining Lalibela: Part 1'
author: "Awash Analytics"
date: "21 Dec 2017"
output: html_document
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: DarkRed;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
  margin-bottom: 50px;
}

div.screenshot {
  width: 950px;
  height: 350px;
  margin-top: 30px;
  margin-bottom: 125px;
}

p {
  margin-top: 20px;
  margin-bottom: 20px;
}

div.img {
  margin-top: 20px;
  margin-bottom: 20px;
}

</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div id="intro">
<h4>Introduction</h4>
<p>
In this blog post, I would like to show you how I scrapped TripAdvisor user reviews for one of tourist destination place in Ethiopia called Lalibela. This is the link for the reviews:
<https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html>
</p>
</div> <!-- end introduction -->

<div id="mainRCode-area">

<h4>Web Scrapping: Reading reviews about Attraction site from TripAdvisor</h4>

```{r, eval=TRUE, message=F, warning=F}
################################
## Environmental settings.    ##
################################
## Set the working directory
# setwd("./TripAdvisor/tourism/")

## Install and load library
library(xml2)         ## to use the READ_HTML function
library(rvest)        ## for all other utilities used for Web Scrapping. Please see package documentation
library(stringr)      ## for regular expression (regex)
library(readr)        ## for import/export of data
library(dplyr)        ## for data manipulation
library(magrittr)     ## for the pipe operator

# options(knitr.table.format = "markdown")
options(knitr.table.format = "html")

###################################################
## Reading reviews of an attraction site.       ##
###################################################
## Load custom source codes
source("./functions/get_10Reviews.R")
source("./functions/get_allReviews_v2.R")

## Get reviews about Lalibela, Ethiopia
reviews_lalibela <- get_allReviews(nbr_page = 2, 
                                   site_gCode = "480193", site_dCode = "324957", 
                                   site_name = "Rock_Hewn_Churches_of_Lalibela", 
                                   site_geoLocation = "Lalibela_Amhara_Region"
                                   )
```

```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_lalibela[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F,
             caption = "Table 1. TripAdvisor reviews about Lalibela, Ethiopia .") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```


```{r, eval=TRUE, message=F}
## Get reviews about Axum, Ethiopia
reviews_axum <- get_allReviews(nbr_page = 2, 
                               site_gCode = "3667784", site_dCode = "324991", 
                               site_name = "The_Ruins_of_Aksum", 
                               site_geoLocation = "Axum_Tigray_Region"
                               )
```

```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_axum[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F,
             caption = "Table 2. TripAdvisor reviews about Axum, Ethiopia .") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```

```{r, eval=TRUE, message=F}
## Get reviews about Mount Kenya, Kenya
reviews_mountKenya <- get_allReviews(nbr_page = 2, 
                                     site_gCode = "319715", site_dCode = "1936998", 
                                     site_name = "Mount_Kenya", 
                                     site_geoLocation = "Mount_Kenya_National_Park"
                                     )
```


```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_mountKenya[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F,
             caption = "Table 3. TripAdvisor reviews about Mount Kenya, Kenya .") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```


```{r, eval=TRUE, message=F}
## Get reviews about Louvre Museum, Paris, France
reviews_louvreMuseum <- get_allReviews(nbr_page = 2, 
                                       site_gCode = "187147", site_dCode = "188757", 
                                       site_name = "Louvre_Museum", 
                                       site_geoLocation = "Paris_Ile_de_France"
                                       )
```


```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_louvreMuseum[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F,
             caption = "Table 4. TripAdvisor reviews about Louvre museum, France .") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```


```{r, eval=FALSE}
#######################################################
## Export final reviews data as a CSV file format.   ##
#######################################################
## Define filename
site_name <- "lalibela"
filename_reviews <- paste("./output/rawdata/reviews_TripAdvisor-", site_name, "_",
                          format(Sys.Date(), format="%B_%d_%Y"), 
                          ".csv", 
                          sep = "")

## Export reviews data
readr::write_csv(x = reviews_lalibela, path = file.path(filename_reviews))
```

</div> <!-- mainRCode-area -->

<div id="get_10Reviews-area">
<h4>The mini R program: Reading the Ten (10) Reviews</h4>


```{r, eval=FALSE}
#' 
#' Extracts all components of a review such as review title, date, location, device, etc.
#' 
#' @param node the single review given by a user
#' 
#' @references 
#' Inspired by Hadley Wickham (author of pkg::rvest) and BjaRule (StackOverflow).
#' https://github.com/hadley/rvest/issues/12
#' https://stackoverflow.com/questions/33250826/scraping-with-rvest-complete-with-nas-when-tag-is-not-present
#' 
#' @author Awash Analytics (December 2017)
#' 
#' @seealso The main program get_allReviews.R make use of this program to extract all the components of a given review.
#' 
#' 

get_10Reviews <- function(node) {

  ## Get current node/row
  node_current <- node
  
  ##########################
  ## Extract all columns  ##
  ##########################
  ## review title
  tmp_title <- node_current %>%
    rvest::html_node(".noQuotes") %>%
    rvest::html_text() 
  
  ## review title
  tmp_fullReview <- node_current %>%
    rvest::html_node(".partial_entry") %>%
    rvest::html_text() 
  
  ## review date
  tmp_date <- node_current %>%
    rvest::html_node(".relativeDate") %>%
    rvest::html_text() %>%
    stringr::str_replace(pattern = "(Reviewed)", replacement = "") %>%   ## removes the text "reviews"
    stringr::str_trim() 
  
  ## reviewer username
  tmp_userName <- node_current %>%
    rvest::html_node(".scrname") %>%
    rvest::html_text()
  
  ## reviewer location
  tmp_userLocation <- node_current %>%
    rvest::html_node(css = ".userLocation") %>%
    html_text()
  
  ## reviewer country of origin, probably a city
  tmp_device <- node_current %>%
    rvest::html_node(".viaMobile") %>%
    rvest::html_text()
  
  ##############################################################
  ## Create final dataframe.                                  ##
  ##############################################################
  ## ** A null value is filled whenever no value is returned  ##
  ##    from Web Scrapping step.                              ##
  ##############################################################
  data.frame(
    title = ifelse(length(tmp_title) == 0, NA,       ## the IFELSE function is used to fill NA whenever HTML_NODES is not able to return a value
                   tmp_title),
    full_review = ifelse(length(tmp_fullReview) == 0, NA,
                         tmp_fullReview),
    date = ifelse(length(tmp_date) == 0, NA,
                  tmp_date),
    user_name = ifelse(length(tmp_userName) == 0, NA,
                      tmp_userName),
    user_device = ifelse(length(tmp_device) == 0, NA,
                    tmp_device),
    user_location = ifelse(length(tmp_userLocation) == 0, NA,      
                                 tmp_userLocation),
    stringsAsFactors=F
  )
}
```
</div> <!-- get_10Reviews-area -->


<div id="get_allReviews-area">
<h4>The magic of patterns: Reading all pages</h4>

```{r, eval=FALSE}
#' 
#' Extracts reviews of an attraction site posted by tourists on TripAdvisor website.
#' It takes care of both a single page and multiple pages.
#' 
#' @param nbr_page the number of pages to grab.
#' @param site_gCode the "g" code as defined by TripAdvisor pagination. Please see the example below.
#' @param site_dCode the "d" code as defined by TripAdvisor pagination. Please see the example below.
#' @param site_name the name of an attraction site.
#' @param site_geoLocation the geographical location of an attraction site. Not that this is not related to a latitude/longitude values. Please see the example below.
#' 
#' @describe This source code calls get_10Reviews.R program to extract the required components (e.g., review title, date, device). Depending on
#' a user request, it can also loop through multiple pages. Finally, it adds extra columns (e.g., attraction location, number of reviews, etc) 
#' to existing reviews stored in a dataframe.
#' 
#' @author Awash Analytics (December 2017)
#' 
#' @example reviews_lalibela <- get_allReviews(nbr_page = 2, 
#'                                             site_gCode = "480193", site_dCode = "324957", 
#'                                             site_name = "Rock_Hewn_Churches_of_Lalibela", site_geoLocation = "Lalibela_Amhara_Region"
#'                                             )
#' 

get_allReviews <- function(nbr_page = NULL, 
                           site_gCode = NULL, site_dCode = NULL, 
                           site_name = NULL, site_geoLocation = NULL) {
  
  message("Page extraction is started: ", date())
  
  ## Main TripAdvisor URL
  TripAdvisor_url <- "https://www.tripadvisor.com"
  
  ## loop through reviews page
  for (i in 1:nbr_page) {
    # print(paste("i = ", i, sep = " "))       ## used only for debugging purpose
    
    ## Construct url address associated to the reviews page
    url_extCommon <- paste("/Attraction_Review-g", site_gCode, "-d", site_dCode, "-Reviews-", 
                           sep = "") 
    
    if (i == 1) {
      # reviewHomePg <- "/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region"
      reviewHomePg <- paste(url_extCommon,
                            site_name, "-", site_geoLocation, 
                            sep = "")
      
      TripAdvisor_reviewUrl <- paste(TripAdvisor_url, reviewHomePg, ".html", 
                                           sep = "") 
      
      ## Backup review home address for later use
      TripAdvisor_reviewHomeUrl <- TripAdvisor_reviewUrl
    } 
    else {
      # reviewOtherPg <- paste("/Attraction_Review-g480193-d324957-Reviews-or", i-1, "0-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region",
      #                                 sep = "")
      reviewOtherPg <- paste(url_extCommon, 
                             "or", i-1, "0-", 
                             site_name, "-", site_geoLocation, 
                             sep = "")
      
      TripAdvisor_reviewUrl <- paste(TripAdvisor_url, reviewOtherPg, ".html",
                                           sep = "")
    }
    
    ## Read reviews given about an attraction site 
    TripAdvisor_topic <- xml2::read_html(TripAdvisor_reviewUrl)
    
    ## Get main container which contains a single review
    reviewer_container <- TripAdvisor_topic %>%
      html_nodes("div.review-container")
    
    ## Get all components of reviews (e.g., title, location, device, etc) and loop through the ten (10) reviews
    reviews_data <- lapply(X = reviewer_container, get_10Reviews) %>%
      dplyr::bind_rows()
    
    ## Concatenate reviews obtained from all pages
    if (i == 1) {
      reviews_dataAll = data.frame(page_nbr = i, reviews_data)
    } else {
      reviews_dataAll <- rbind(reviews_dataAll, 
                               data.frame(page_nbr = i, reviews_data))
    }
  }
  
  #############################################################################################################################
  ## Combine reviews data with other variables available in review homepage (e.g., number of reviews, site location, etc).   ##
  #############################################################################################################################
  # TripAdvisor_homePage <- "https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html"
  TripAdvisor_reviewHome <- xml2::read_html(TripAdvisor_reviewHomeUrl)
  
  ## Get total number of reviews given for an attraction site
  total_reviews <- TripAdvisor_reviewHome %>%
    rvest::html_nodes(".seeAllReviews") %>%
    rvest::html_text() %>%
    stringr::str_replace_all(pattern = "(reviews)|(\\\nRead\\s+(all))", replacement = "") %>%   ## removes the text "reviews"
    stringr::str_trim() %>%
    stringr::str_replace(pattern = ",", replacement = "") %>%           ## removes the comma
    as.numeric() %>%
    dplyr::first()          ## In case, multiple values are returned (e.g., "204", "204" which is true for Axum, Ethiopia)
  
  ## get attraction site location
  attraction_location <- TripAdvisor_reviewHome %>%
    rvest::html_node(".address") %>%
    rvest::html_text() 
  
  ## Date for data access
  date_dataAccess <- Sys.Date() %>%
    format(format = "%B %d, %Y")          ## this gives date format like "December 21, 2017"
  
  ## Combine main reviews data and additional info about the site
  reviews_final <- data.frame(attraction_location, total_reviews, 
                              date_dataAccess, reviews_dataAll 
  )
  
  message("Page extraction is completed: ", date())
  
  return(reviews_final)
}
```


</div> <!-- get_allReviews-area -->



```{r, eval=FALSE}
test
```
