---
title: 'Mining Lalibela: Part 1'
author: "Awash Analytics"
date: "21 Dec 2017"
output: html_document
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: DarkRed;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
  margin-bottom: 50px;
}

div.screenshot {
  width: 950px;
  height: 350px;
  margin-top: 30px;
  margin-bottom: 125px;
}

p {
  margin-top: 20px;
  margin-bottom: 20px;
}

div.img {
  margin-top: 20px;
  margin-bottom: 20px;
}

div.myCaption {
  margin-top: 10px;
  margin-bottom: 3px;
}

</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div id="intro">
<!-- <h4>1. Introduction</h4> -->
## Introduction

<p>
In this article I explain how I managed to scrape <a target="_blank" href="https://www.tripadvisor.com/Attractions">TripAdvisor</a> for reviews of tourists about attraction sites (e.g., Lalibel, Ethiopia and Louvre museum, Paris). The R program manages to grab review details such as date of review, reviewer country, title (which is interesting for Sentiment Analysis), device (via Mobile device or not), etc. Let's get started.
</p>

</div> <!-- end introduction -->

<div id="get_10Reviews-area">
<!-- <h4>2. Scraping TripAdvisor Review Components</h4> -->
## Scraping Review Attributes

<p>
The ``get_10Reviews`` function extracts the required components / attributes of a review such as review title, description, date, name, location, and device. For the CSS selector, I used a tool called <a target="_blank" href="https://chrome.google.com/webstore/detail/selectorgadget/mhjhnkcfbdhnjickkkdbjoemdmbfginb?hl=en">SelectorGadget</a>. For the web scraping part I used mainly the ``rvest`` package - Thanks to Hadley Wickham. 

The ``get_10Reviews`` function has one argument called "node". This represents a single review given by the user, and its value is set by the other program which will be discussed later.

For text processing I used functions available in the ``stringr`` package. When I scrape the review date, for example, an extra character ("Reviewed") was included. Thus, as shown in the code below I used ``stringr::str_replace`` function to remove the extra string. 

The ``rvest`` package returns "0" when no value is returned from the web. That is the reason for using the ``ifelse`` function in the last part of the code below. This will help you to get the same number of reviews. Otherwise, less number of reviews will be extracted because of missing values. I hope this issue will be resolved by the developer of the ``rvest`` package soon.
</p>

<div class="myCaption">
*Code 1: The R program responsible for grabbing the required components of a given review (e.g., reviewer title, date, device, location, etc).*
</div>
```{r, eval=FALSE}
#' 
#' Extracts all components of a review such as review title, date, location, device, etc.
#' 
#' @param node the single review given by a user
#' 
#' @references 
#' Inspired by Hadley Wickham (author of pkg::rvest) and BjaRule (StackOverflow).
#' https://github.com/hadley/rvest/issues/12
#' https://stackoverflow.com/questions/33250826/scraping-with-rvest-complete-with-nas-when-tag-is-not-present
#' 
#' @author Awash Analytics (December 2017)
#' 
#' @seealso The main program get_allReviews.R make use of this program to extract all the components of a given review.
#' 
#' 

get_10Reviews <- function(node) {

  ## Get current node/row
  node_current <- node
  
  ##########################
  ## Extract all columns  ##
  ##########################
  ## review title
  tmp_title <- node_current %>%
    rvest::html_node(".noQuotes") %>%
    rvest::html_text() 
  
  ## review title
  tmp_fullReview <- node_current %>%
    rvest::html_node(".partial_entry") %>%
    rvest::html_text() 
  
  ## review date
  tmp_date <- node_current %>%
    rvest::html_node(".relativeDate") %>%
    rvest::html_text() %>%
    stringr::str_replace(pattern = "(Reviewed)", replacement = "") %>%   ## removes the text "reviews"
    stringr::str_trim() 
  
  ## reviewer username
  tmp_userName <- node_current %>%
    rvest::html_node(".scrname") %>%
    rvest::html_text()
  
  ## reviewer location
  tmp_userLocation <- node_current %>%
    rvest::html_node(css = ".userLocation") %>%
    html_text()
  
  ## reviewer country of origin, probably a city
  tmp_device <- node_current %>%
    rvest::html_node(".viaMobile") %>%
    rvest::html_text()
  
  ##############################################################
  ## Create final dataframe.                                  ##
  ##############################################################
  ## ** A null value is filled whenever no value is returned  ##
  ##    from Web Scrapping step.                              ##
  ##############################################################
  data.frame(
    title = ifelse(length(tmp_title) == 0, NA,       ## the IFELSE function is used to fill NA whenever HTML_NODES is not able to return a value
                   tmp_title),
    full_review = ifelse(length(tmp_fullReview) == 0, NA,
                         tmp_fullReview),
    date = ifelse(length(tmp_date) == 0, NA,
                  tmp_date),
    user_name = ifelse(length(tmp_userName) == 0, NA,
                      tmp_userName),
    user_device = ifelse(length(tmp_device) == 0, NA,
                    tmp_device),
    user_location = ifelse(length(tmp_userLocation) == 0, NA,      
                                 tmp_userLocation),
    stringsAsFactors=F
  )
}
```
</div> <!-- get_10Reviews-area -->


<div id="get_allReviews-area">
<!-- <h4>3. How to scrap all reviews (in a page or multiple pages)?</h4> -->
## How to scrap all reviews (in a page or multiple pages)?

<p>
The above code handles an individual review at a time and extracts the required attributes of the review. However, there are a total of ten (10) reviews per page. For example, <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">TripAdvisor - Lalibela</a>. 

The ``get_allReviews`` function handles grabing reviews from a single page or multiple pages. The user of the function can specify the number of pages to scrape using the "nbr_page" argument. 

The values of the other arguments (such as "site_gCode", "site_dCode", "site_name", and "site_geoLocation") are available for you in url of the attraction site. For <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">TripAdvisor - Lalibela</a> attraction site, for example, the values are defined as: ``site_gCode = "480193"``, ``site_dCode = "324957"``, ``site_name = "Rock_Hewn_Churches_of_Lalibela"``, and ``site_geoLocation = "Lalibela_Amhara_Region"``. In the application section different attraction sites are used for demonstration purpose (e.g., Louvre museum, Paris and Mount Kenya, Kenya).
</p>


<div class="myCaption">
*Code 2: The R program responsible for grabbing all reviews available in a single page or multiple pages.*
</div>
```{r, eval=FALSE}
#' 
#' Extracts reviews of an attraction site posted by tourists on TripAdvisor website.
#' It takes care of both a single page and multiple pages.
#' 
#' @param nbr_page the number of pages to grab.
#' @param site_gCode the "g" code as defined by TripAdvisor pagination. Please see the example below.
#' @param site_dCode the "d" code as defined by TripAdvisor pagination. Please see the example below.
#' @param site_name the name of an attraction site.
#' @param site_geoLocation the geographical location of an attraction site. Not that this is not related to a latitude/longitude values. Please see the example below.
#' 
#' @describe This source code calls get_10Reviews.R program to extract the required components (e.g., review title, date, device). Depending on
#' a user request, it can also loop through multiple pages. Finally, it adds extra columns (e.g., attraction location, number of reviews, etc) 
#' to existing reviews stored in a dataframe.
#' 
#' @author Awash Analytics (December 2017)
#' 
#' @example reviews_lalibela <- get_allReviews(nbr_page = 2, 
#'                                             site_gCode = "480193", site_dCode = "324957", 
#'                                             site_name = "Rock_Hewn_Churches_of_Lalibela", site_geoLocation = "Lalibela_Amhara_Region"
#'                                             )
#' 

get_allReviews <- function(nbr_page = NULL, 
                           site_gCode = NULL, site_dCode = NULL, 
                           site_name = NULL, site_geoLocation = NULL) {
  
  message("Page extraction is started: ", date())
  
  ## Main TripAdvisor URL
  TripAdvisor_url <- "https://www.tripadvisor.com"
  
  ## loop through reviews page
  for (i in 1:nbr_page) {
    # print(paste("i = ", i, sep = " "))       ## used only for debugging purpose
    
    ## Construct url address associated to the reviews page
    url_extCommon <- paste("/Attraction_Review-g", site_gCode, "-d", site_dCode, "-Reviews-", 
                           sep = "") 
    
    if (i == 1) {
      # reviewHomePg <- "/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region"
      reviewHomePg <- paste(url_extCommon,
                            site_name, "-", site_geoLocation, 
                            sep = "")
      
      TripAdvisor_reviewUrl <- paste(TripAdvisor_url, reviewHomePg, ".html", 
                                           sep = "") 
      
      ## Backup review home address for later use
      TripAdvisor_reviewHomeUrl <- TripAdvisor_reviewUrl
    } 
    else {
      # reviewOtherPg <- paste("/Attraction_Review-g480193-d324957-Reviews-or", i-1, "0-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region",
      #                                 sep = "")
      reviewOtherPg <- paste(url_extCommon, 
                             "or", i-1, "0-", 
                             site_name, "-", site_geoLocation, 
                             sep = "")
      
      TripAdvisor_reviewUrl <- paste(TripAdvisor_url, reviewOtherPg, ".html",
                                           sep = "")
    }
    
    ## Read reviews given about an attraction site 
    TripAdvisor_topic <- xml2::read_html(TripAdvisor_reviewUrl)
    
    ## Get main container which contains a single review
    reviewer_container <- TripAdvisor_topic %>%
      html_nodes("div.review-container")
    
    ## Get all components of reviews (e.g., title, location, device, etc) and loop through the ten (10) reviews
    reviews_data <- lapply(X = reviewer_container, get_10Reviews) %>%
      dplyr::bind_rows()
    
    ## Concatenate reviews obtained from all pages
    if (i == 1) {
      reviews_dataAll = data.frame(page_nbr = i, reviews_data)
    } else {
      reviews_dataAll <- rbind(reviews_dataAll, 
                               data.frame(page_nbr = i, reviews_data))
    }
  }
  
  #############################################################################################################################
  ## Combine reviews data with other variables available in review homepage (e.g., number of reviews, site location, etc).   ##
  #############################################################################################################################
  # TripAdvisor_homePage <- "https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html"
  TripAdvisor_reviewHome <- xml2::read_html(TripAdvisor_reviewHomeUrl)
  
  ## Get total number of reviews given for an attraction site
  total_reviews <- TripAdvisor_reviewHome %>%
    rvest::html_nodes(".seeAllReviews") %>%
    rvest::html_text() %>%
    stringr::str_replace_all(pattern = "(reviews)|(\\\nRead\\s+(all))", replacement = "") %>%   ## removes the text "reviews"
    stringr::str_trim() %>%
    stringr::str_replace(pattern = ",", replacement = "") %>%           ## removes the comma
    as.numeric() %>%
    dplyr::first()          ## In case, multiple values are returned (e.g., "204", "204" which is true for Axum, Ethiopia)
  
  ## get attraction site location
  attraction_location <- TripAdvisor_reviewHome %>%
    rvest::html_node(".address") %>%
    rvest::html_text() 
  
  ## Date for data access
  date_dataAccess <- Sys.Date() %>%
    format(format = "%B %d, %Y")          ## this gives date format like "December 21, 2017"
  
  ## Combine main reviews data and additional info about the site
  reviews_final <- data.frame(attraction_location, total_reviews, 
                              date_dataAccess, reviews_dataAll 
  )
  
  message("Page extraction is completed: ", date())
  
  return(reviews_final)
}
```

</div> <!-- get_allReviews-area -->


<div id="main-application-area">
<!-- <h4>4. Application</h4> -->
## Application

<p>
Now I'll explain usage of the functions I built for scraping <a target="_blank" href="https://www.tripadvisor.com/Attractions">TripAdvisor</a> using four attraction sites such as <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g187147-d188757-Reviews-Louvre_Museum-Paris_Ile_de_France.html">Louvre museum - Paris</a>, <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g319715-d1936998-Reviews-Mount_Kenya-Mount_Kenya_National_Park.html">Mount Kenya - Kenya</a>, <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g3667784-d324991-Reviews-The_Ruins_of_Aksum-Axum_Tigray_Region.html">Axum - Ethiopia</a>, and <a target="_blank" href="https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html">Lalibela - Ethiopia</a>.
</p>


<div class="myCaption">
*Code 3: The main R program which shows usage of the custom functions. For demonstration purpose, four attraction sites are selected: Lalibela, Axum, Mount Kenya and Louvre museum.*
</div>

```{r, eval=TRUE, message=F, warning=F}
################################
## Environmental settings.    ##
################################
## Set the working directory
# setwd("./TripAdvisor/tourism/")

## Install and load library
library(xml2)         ## to use the READ_HTML function
library(rvest)        ## for all other utilities used for Web Scrapping. Please see package documentation
library(stringr)      ## for regular expression (regex)
library(readr)        ## for import/export of data
library(dplyr)        ## for data manipulation
library(magrittr)     ## for the pipe operator

# options(knitr.table.format = "markdown")
options(knitr.table.format = "html")

###################################################
## Reading reviews of an attraction site.       ##
###################################################
## Load custom source codes
source("./functions/get_10Reviews.R")
source("./functions/get_allReviews_v2.R")

## Get reviews about Lalibela, Ethiopia
reviews_lalibela <- get_allReviews(nbr_page = 2, 
                                   site_gCode = "480193", site_dCode = "324957", 
                                   site_name = "Rock_Hewn_Churches_of_Lalibela", 
                                   site_geoLocation = "Lalibela_Amhara_Region"
                                   )
```

<p>
For demonstration purpose, I selected four attraction sites such as Lalibela and Axum (found in Ethiopia, Africa), Mount Kenya (Kenya, Africa), and Louvre museum (Paris, France).

Here is the link with all reviews about Lalibela which is one of the most famous tourist destination found in Ethiopia, Africa:
<https://www.tripadvisor.com/Attraction_Review-g480193-d324957-Reviews-Rock_Hewn_Churches_of_Lalibela-Lalibela_Amhara_Region.html>
</p>

<div class="myCaption">
*Table 1. Tourist reviews about Lalibela, Ethiopia.*
</div>
```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_lalibela[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```

<div class="myCaption">
*Code 4: Reading TripAdvisor for reviews about Axum, Ethiopia.*
</div>
```{r, eval=TRUE, message=F}
## Get reviews about Axum, Ethiopia
reviews_axum <- get_allReviews(nbr_page = 2, 
                               site_gCode = "3667784", site_dCode = "324991", 
                               site_name = "The_Ruins_of_Aksum", 
                               site_geoLocation = "Axum_Tigray_Region"
                               )
```

<div class="myCaption">
*Table 2. Tourist reviews about Axum, Ethiopia.*
</div>
```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_axum[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```

<div class="myCaption">
*Code 5: Reading TripAdvisor for reviews about Mount Kenya, Kenya*
</div>
```{r, eval=TRUE, message=F}
## Get reviews about Mount Kenya, Kenya
reviews_mountKenya <- get_allReviews(nbr_page = 2, 
                                     site_gCode = "319715", site_dCode = "1936998", 
                                     site_name = "Mount_Kenya", 
                                     site_geoLocation = "Mount_Kenya_National_Park"
                                     )
```


<div class="myCaption">
*Table 3. Tourist reviews about Mount Kenya, Kenya.*
</div>
```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_mountKenya[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```


<div class="myCaption">
*Code 4: Reading TripAdvisor for reviews about Louvre museum, France.*
</div>
```{r, eval=TRUE, message=F}
## Get reviews about Louvre Museum, Paris, France
reviews_louvreMuseum <- get_allReviews(nbr_page = 2, 
                                       site_gCode = "187147", site_dCode = "188757", 
                                       site_name = "Louvre_Museum", 
                                       site_geoLocation = "Paris_Ile_de_France"
                                       )
```

<div class="myCaption">
*Table 4. Tourist reviews about Louvre museum, France.*
</div>
```{r, eval=TRUE, message=F, echo=FALSE}
knitr::kable(psych::headTail(reviews_louvreMuseum[, c("attraction_location",  "total_reviews", "page_nbr", "title", "date", "user_device", "user_location")], ellipsis = F), row.names = F) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive",
                                                  full_width = T, position = "left"))
```

</div>  <!-- end main-application-area -->

<div id="export-rawdata">
<!-- <h4>5. Conclusion</h4> -->
## Conclusion

<div class="myCaption">
*Code 5: Export reviews rawdata for future analysis such as sentiment analysis and visualization.*
</div>
```{r, eval=FALSE}
#######################################################
## Export final reviews data as a CSV file format.   ##
#######################################################
## Define filename
site_name <- "lalibela"
filename_reviews <- paste("./output/rawdata/reviews_TripAdvisor-", site_name, "_",
                          format(Sys.Date(), format="%B_%d_%Y"), 
                          ".csv", 
                          sep = "")

## Export reviews data
readr::write_csv(x = reviews_lalibela, path = file.path(filename_reviews))
```

</div> <!-- end export-rawdata -->






```{r, eval=FALSE}
test
```
